Non-kissing and non-crossing complexes \\ for gentle algebras

### 2018-05-23 draft/accordionComplexSurfaces.tex
Tentative de definition d'accordeon.

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is an arc of~$(\surface, B)$ so that for each face~$f \in \faces(\dissection)$ ...
\end{definition}

>>>>

\begin{definition}
\label{def:accordion}
A \defn{$\dissection$-accordion} is an arc~$\gamma$ of~$(\surface, B)$ such that any two arcs of $\dissection$ crossed consecutively by~$\gamma$
share a marked point with the property that the region bounded by~$\gamma$ and the two arcs around the marked point is homeomorphic to a disk
(in particular, it contains no punctures).
\end{definition}
